Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-01-21 manuscripts/manuscript.Rmd
fix misplaced quote string

```{r}
fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment. Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials. Dockside revenues are always higher than adjustment costs.  When those costs are not accounted for in the policy ("no adjustment costs"), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
```

>>>>

```{r}
fig5_caption <- paste("Distribution of revenues from fishing and costs paid to adjustment. Plot shows distributions for the linear costs structure ($\\Pi_1$) only, alternate penalties can be found in the supplementary materials. Dockside revenues are always higher than adjustment costs.  When those costs are not accounted for in the policy ('no adjustment costs'), it is possible to obtain only marginally higher revenues, but pay higher adjustment costs.")
```
